SciPy - some descriptive title here

### 2018-05-31 scipy-1.0/paper.tex
First round of revisions for PR 29.

SciPy adopted an official Code of Conduct on October 24, 2017 (see PR\#7963), drawing
inspiration from the Apache Foundation Code of Conduct, the Contributor Covenant,
the Jupyter Code of Conduct, and the Open Source Guides - Code of Conduct. In short,
we stated five specific guidelines: \emph{be open} (to anyone participating in our community),
\emph{be empathetic and patient} (in resolving conflicts), \emph{be collaborative} (we depend
on each other to build up the tools in the library), \emph{be inquisitive} (identifying issues
early on can be helpful to everyone), and \emph{be careful with wording} (no harassment or
exclusionary behavior). We outline a broad diversity inclusion statement, and provide
instructions for contacting the three members of our Code of Conduct Committee or an
external representative on the NumFOCUS Board of Directors.

>>>>

SciPy adopted an official Code of Conduct on October 24, 2017 (see PR\#7963), drawing
inspiration from the Apache Foundation Code of Conduct, the Contributor Covenant,
the Jupyter Code of Conduct, and the Open Source Guides - Code of Conduct. In short,
we stated five specific guidelines: \emph{be open} (to anyone participating in our community),
\emph{be empathetic and patient} (in resolving conflicts), \emph{be collaborative} (we depend
on each other to build up the tools in the library), \emph{be inquisitive} (identifying issues
early on can be helpful to everyone), and \emph{be careful with wording} (do not harass or exclude).
We outline a broad diversity inclusion statement, and provide
instructions for contacting the three members of our Code of Conduct Committee or an
external representative on the NumFOCUS Board of Directors.
